Erratum: Inference of proto-neutron star properties from gravitational-wave data in core-collapse supernovae [Phys.~Rev.~D 105, 063006 (2021)]

### 2021-11-02 erratum/ccsn_erratum.tex
Updating table

\begin{table}[h]
 \begin{tabular}{crr}
    \hline
    Coefficient & \multicolumn{1}{c}{Estimate} & Standard error \\
    \hline
   $\beta_1$  &  $ 1.00 \times 10^{-06}$ & $2.12 \times 10^{-08}$ \\   
   $\beta_2$  &  $-8.22 \times 10^{-10}$ & $5.00 \times 10^{-11}$ \\
   $\beta_3$  &  $ 1.01 \times 10^{-12}$ & $2.70 \times 10^{-14}$ \\
   $\alpha_0$ &  $-1.02 \times 10^{+01}$ & $6.80 \times 10^{-02}$ \\
   $\alpha_1$ &  $ 7.24 \times 10^{-04}$ & $1.56 \times 10^{-04}$ \\
   $\alpha_2$ &  $ 6.23 \times 10^{-07}$ & $8.15 \times 10^{-08}$ \\   
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.\pcd{[CORRECT NUMBERS IN THE TABLE. JUST A FACTOR 2 iIN ALL COEFFICIENTS?]}}\label{tab:model}
\end{table}

>>>>

\begin{table}[h]
 \begin{tabular}{crr}
    \hline
    Coefficient & \multicolumn{1}{c}{Estimate} & Standard error \\
    \hline
   $\beta_1$  &  $ 2.00 \times 10^{-06}$ & $4.24 \times 10^{-08}$ \\   
   $\beta_2$  &  $-1.64 \times 10^{-9}$ & $1.00 \times 10^{-10}$ \\
   $\beta_3$  &  $ 2.02 \times 10^{-12}$ & $5.40 \times 10^{-14}$ \\
   $\alpha_0$ &  $-9.51 \times 10^{+00}$ & $6.80 \times 10^{-02}$ \\
   $\alpha_1$ &  $ 7.24 \times 10^{-04}$ & $1.56 \times 10^{-04}$ \\
   $\alpha_2$ &  $ 6.23 \times 10^{-07}$ & $8.15 \times 10^{-08}$ \\   
    \hline
  \end{tabular}
\caption{Estimate and standard error of the coefficients of the best fit model describing the ratio $r=M_{\rm PNS}/R_{\rm PNS}^2$ as function of the frequency of the $\mbox{}^2g_2$ mode.\pcd{[CHECK IF NUMBERS ARE CORRECT]}}\label{tab:model}
\end{table}
